Considering scale in multilayer animal social networks

### 2020-06-17 paper/manuscript.Rmd
edit abstract

# Abstract
Scale remains a foundational concept in ecology. Spatial scale, for instance,
has become a central consideration in the way we understand landscape ecology
and animal space use. Meanwhile, social processes can also scale from fine-scale
interactions to co-occurrence to overlapping home ranges, and vary within and 
across seasons. Multilayer networks promise the integration of monolayer
animal social networks with the complexity and importance of animal space use
and movement in heterogeneous landscapes. Despite the complex interplay between
social networks and animal space use, there remains an important biological
and methodological gap in our understanding of an animal’s perception of scale.
Here we discuss the role of scale in the context of multilayer networks and
provide a social ungulate case study to illustrate the role of social, spatial,
and temporal scale on multilayer processes. <!--We also present perspectives on
future development and applications of scale in multilayer networks with respect
to: phenotypes and individual fitness, movement ecology and collective movement,
and habitat selection and space use.--> Effective integration of social and spatial
processes, including biologically meaningful scales, within the context of
animal social networks is an emerging area of research, as such our contribution
incorporates perspectives on how the social environment and spatial processes
are linked across scales in a multilayer context.

>>>>

# Abstract
Scale remains a foundational concept in ecology. Spatial scale, for instance,
has become a central consideration in the way we understand landscape ecology
and animal space use. Meanwhile, social processes can also scale from fine-scale
interactions to co-occurrence to overlapping home ranges and vary within and 
across seasons. Multilayer networks promise the integration of monolayer
animal social networks with the complexity and importance of animal space use
and movement in heterogeneous landscapes. Despite the complex interplay between
social networks and animal space use, there remains an important biological
and methodological gap in our understanding of an animal’s perception of scale.
Here we discuss the role of scale in the context of multilayer networks and
provide a social ungulate case study to illustrate the role of social, spatial,
and temporal scale on multilayer processes. <!--We also present perspectives on
future development and applications of scale in multilayer networks with respect
to: phenotypes and individual fitness, movement ecology and collective movement,
and habitat selection and space use.--> Effective integration of social and spatial
processes, including biologically meaningful scales, within the context of
animal social networks is an emerging area of research. Here, we
incorporate perspectives on how the social environment and spatial processes
are linked across scales in a multilayer context.
